CF Registry Analysis

### 2022-12-16 Christine Chan/CF Registry/cf_registry_analysis.qmd
CFRD incidence

```{r}
library(table1)
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(table1)
# All data
df = read.csv("/home/timvigers/Work/CHCO/Christine Chan/CF registry data/CFF19_encountersMerged_Del1.csv",na.strings = c("","N/A"))
df = df %>% arrange(eDWID,reviewyear,encounternum)
# For those with CFRD by OGTT, find first visit with diagnosis
first_cfrd = df %>% group_by(eDWID) %>% 
  summarise(first_cfrd = which(twohour_bloodglucose >= 200),.groups = "drop")
df = left_join(df,first_cfrd,by = "eDWID")
df = df %>% group_by(eDWID) %>% 
  mutate(cfrd_ogtt = case_when(
    row_number() < first_cfrd ~ "No",
    row_number() >= first_cfrd ~ "Yes"
  )) %>%
  ungroup()
df$cfrd_ogtt[is.na(df$cfrd_ogtt)] = "No"
df$cfrd_ogtt = factor(df$cfrd_ogtt,levels = c("No","Yes"),
                      labels = c("No","Yes"),ordered = TRUE)
# Testing
t = df %>% select(eDWID,reviewyear,)
```

```{r}
#| @tbl-incidence
t = df %>% 
  group_by(eDWID,reviewyear) %>% 
  summarise(cfrd_ogtt = max(cfrd_ogtt),.groups = "drop") %>% 
  group_by(reviewyear) %>%
  summarise(cfrd_rate = mean(as.numeric(cfrd_ogtt)-1))
```
